Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2017-07-23 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor changes

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection 1)')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn7501880';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

@@

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection 1)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - Sparse Model')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn9846623';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (ACC and DLPFC)';

@@

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - Sparse Model", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

### 2017-07-23 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor changes

tmp = de.hbcc %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue1, logFC) %>%
  group_by(Comparison, Tissue1) %>%
  dplyr::summarise(FDR_0_05_UP = length(unique(ensembl_gene_id[logFC > 0])),
                   FDR_0_05_DOWN = length(unique(ensembl_gene_id[logFC < 0])))

tmp1 = de.hbcc %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue1, logFC) %>%
  group_by(Comparison, Tissue1) %>%
  dplyr::summarise(FDR_0_05_FC_1.2_UP = length(unique(ensembl_gene_id[logFC > log2(1.2)])),
                   FDR_0_05_FC_1.2_DOWN = length(unique(ensembl_gene_id[logFC < -log2(1.2)])))

@@

### Gene set enrichment analysis
Using Fisher's exact test for gene set enrichment analysis
```{r enrich.de, fig.height=16, fig.width=16}
diffexp.genes = de.hbcc %>%
  dplyr::mutate(Direction = sign(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP'))) %>%
  dlply(.(Comparison, Tissue1, Direction), .fun = function(x){
    tmp = x$hgnc_symbol[x$adj.P.Val <= 0.05] %>% unique
    tmp = tmp[!is.na(tmp)]
  })
diffexp.genes = diffexp.genes[sapply(diffexp.genes, length) > 20]
backgroundGenes = unique(DE$hgnc_symbol)

>>>>

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue1, logFC) %>%
  group_by(Comparison, Tissue1) %>%
  dplyr::summarise(FDR_0_05_UP = length(unique(ensembl_gene_id[logFC > 0])),
                   FDR_0_05_DOWN = length(unique(ensembl_gene_id[logFC < 0])))

tmp1 = DE %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue1, logFC) %>%
  group_by(Comparison, Tissue1) %>%
  dplyr::summarise(FDR_0_05_FC_1.2_UP = length(unique(ensembl_gene_id[logFC > log2(1.2)])),
                   FDR_0_05_FC_1.2_DOWN = length(unique(ensembl_gene_id[logFC < -log2(1.2)])))

@@

### Gene set enrichment analysis
Using Fisher's exact test for gene set enrichment analysis
```{r enrich.de, fig.height=16, fig.width=16}
diffexp.genes = DE %>%
  dplyr::mutate(Direction = sign(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP'))) %>%
  dlply(.(Comparison, Tissue1, Direction), .fun = function(x){
    tmp = x$hgnc_symbol[x$adj.P.Val <= 0.05] %>% unique
    tmp = tmp[!is.na(tmp)]
  })
diffexp.genes = diffexp.genes[sapply(diffexp.genes, length) > 20]
backgroundGenes = unique(DE$hgnc_symbol)
